Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-24 VMCAI-revised-version/final.tex
up

\begin{center}
\resizebox{\textwidth}{!}{
\begin{tabular}{ | l | c | c | c | r |}
\hline   \ 
		& $\Safe = {\uparrow \Safe}$~ 
		 & $\Safe = {\downarrow \Safe}$~ 
 \\ \hline
   \multirow{3}{*}{RP} 
  	& WBTS (post-ideal-effective) Thm~\ref{down-up}
   		 & Downard-WSTS (pred*-basis-effective) Thm~\ref{up-down} \\ 
~	& WBTS (pred-basis-effective) Thm~\ref{xxx}
		& VASS \\\cline{2-3}
~	& WSTS (post-effective) Prop~\ref{indec WSTS} & WSTS (pred-basis-effective) Prop~\ref{indec WSTS with dcs}    \\ \hline
   \multirow{3}{*}{BRP} 
  	& WBTS (post-ideal-effective) Thm~\ref{down-up}
   		 & ? \\ 
~	& WBTS (pred-basis-effective) Thm~\ref{xxx}
		& (VASS ici aussi) \\\cline{2-3}
~	& ? & ?    \\ \hline
   \multirow{3}{*}{kRP} 
 	& WBTS (post-ideal-effective) Thm~\ref{down-up} 
   		 & ? \\ 
~	& WBTS (pred-basis-effective) Thm~\ref{xxx}
		& (VASS ici aussi) \\\cline{2-3}
~	& ? & ?    \\ \hline

   \multirow{2}{*}{sRP} 
  	& WBTS (post-ideal-effective) Thm~\ref{post srp}
   		 & WSTS (downard + upward) Thm~9 \\ \cline{2-3}
~	& WSTS (pred-...) Prop~\ref{srp up down} & WSTS (pred-basis + ??) Prop~\ref{srp up down}    \\ \hline
   \multirow{2}{*}{BsRP} 
  	& WBTS (pred + post*-ideal-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & WSTS (d+up) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS (pred-...) Prop~\ref{srp up down} & ?    \\ \hline
   \multirow{2}{*}{ksRP} 
  	& WBTS (pred + post*-ideal-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & WSTS (d+up) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS (pred-...) Prop~\ref{srp up down} & ?    \\ \hline

@@

To obtain decidability results, we must introduce some notions of \emph{effectiveness}. We use a mixture of the notions defined both by Blondin and al. in \cite{DBLP:journals/lmcs/BlondinFM17}) and by Halfon in \cite{DBLP:phd/hal/Halfon18}.
%			 that will be essential for solving various resilience problems in different models of WSTS. 
First, to simplify, we suppose that all classes of considered ordered transition systems $\mathscr{S}=(S, \rightarrow, \leq)$ satisfy the five following properties:
\begin{enumerate}
\item there exists an algorithm that decides whether $s \rightarrow t$ is true or not, for any states $s,t \in S$,
%
\item there is a computational representation for $S$ for which membership in $S$ is decidable,
%
%			We also suppose that all considered wqos $(S,\leq)$ satisfy the three following conditions : 
\item $\leq$ is decidable,
\item there is a computational representation for $Ideals(S)$ for which membership in $Ideals(S)$ is decidable, and
\item  inclusion of ideals is decidable. 
\end{enumerate}
%
Blondin and al. showed (Lemma 4.3 in \cite{DBLP:journals/lmcs/BlondinFM17}) that under the previous hypotheses, one are able to enumerate \emph{downward-closed sets} (by their finite decomposition in ideals), to decide inclusion between downward-closed sets and to decide if a state belongs to a given finite set of ideals. But the five properties are not sufficient to compute the complementary and the intersection of downward-closed sets.
%
Halfon introduced \emph{ideally-effective wqo} as wqo that essentially allow to compute representations of (principal) ideals $\mathop{\downarrow} s$, of the complementary of an ideal, of the complementary of filters (a filter is a set $\mathop{\uparrow} s$ for $s \in S$) and to compute representations of finite intersections of filters and finite intersections of ideals. Most well-known wqo are ideally-effective . \cite{DBLP:phd/hal/Halfon18}.
%	 (hence of downward-closed sets).

>>>>

\begin{center}
\resizebox{\textwidth}{!}{
\begin{tabular}{ | l | c | c | c | r |}
\hline   \ 
		& $\Safe = {\uparrow \Safe}$~ 
		 & $\Safe = {\downarrow \Safe}$~ 
 \\ \hline
   \multirow{3}{*}{RP} 
  	& WBTS ($\post$-ideal-effective) Thm~\ref{down-up}
   		 & Downard-WSTS ($\pred^*$-basis-effective) Thm~\ref{up-down} \\ 
~	& WBTS ($\pred$-basis-effective) Thm~\ref{xxx}
		& VASS \\\cline{2-3}
~	& WSTS ($\post$-effective) Prop~\ref{indec WSTS} & WSTS ($\pred$-basis-effective) Prop~\ref{indec WSTS with dcs}    \\ \hline
   \multirow{3}{*}{BRP} 
  	& WBTS ($\post$-ideal-effective) Thm~\ref{down-up}
   		 & ? \\ 
~	& WBTS ($\pred$-basis-effective) Thm~\ref{xxx}
		& (VASS ici aussi) \\\cline{2-3}
~	& ? & ?    \\ \hline
   \multirow{3}{*}{kRP} 
 	& WBTS ($\post$-ideal-effective) Thm~\ref{down-up} 
   		 & ? \\ 
~	& WBTS ($\pred$-basis-effective) Thm~\ref{xxx}
		& (VASS ici aussi) \\\cline{2-3}
~	& ? & ?    \\ \hline

   \multirow{2}{*}{sRP} 
  	& WBTS ($\post$-ideal-effective) Thm~\ref{post srp}
   		 & WSTS (downard + upward) Thm~9 \\ \cline{2-3}
~	& WSTS ($\pred$-...) Prop~\ref{srp up down} & WSTS ($\pred$-basis + ??) Prop~\ref{srp up down}    \\ \hline
   \multirow{2}{*}{BsRP} 
  	& WBTS ($\pred$ + $\post^*$-ideal-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889} 
   		 & WSTS (d+up) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-...) Prop~\ref{srp up down} & ?    \\ \hline
   \multirow{2}{*}{ksRP} 
  	& WBTS ($\pred$ + $\post^*$-ideal-effective) Thm~\ref{ref ozkan} \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}  
   		 & WSTS (d+up) Cor~\ref{downward brp} \\ \cline{2-3}
~	& WSTS ($\pred$-...) Prop~\ref{srp up down} & ?    \\ \hline

@@

To obtain decidability results, we must introduce some notions of \emph{effectiveness}. We use a mixture of the notions defined both by Blondin and al. in \cite{DBLP:journals/lmcs/BlondinFM17} and by Halfon in \cite{DBLP:phd/hal/Halfon18}.
%			 that will be essential for solving various resilience problems in different models of WSTS. 
First, to simplify, we suppose that all classes of considered ordered transition systems $\mathscr{S}=(S, \rightarrow, \leq)$ satisfy the five following properties:
\begin{enumerate}
\item there exists an algorithm that decides whether $s \rightarrow t$ is true or not, for any states $s,t \in S$,
%
\item there is a computational representation for $S$ for which membership in $S$ is decidable,
%
%			We also suppose that all considered wqos $(S,\leq)$ satisfy the three following conditions : 
\item $\leq$ is decidable,
\item there is a computational representation for $Ideals(S)$ for which membership in $Ideals(S)$ is decidable, and
\item  inclusion of ideals is decidable. 
\end{enumerate}
%
Blondin and al. showed (Lemma 4.3 in \cite{DBLP:journals/lmcs/BlondinFM17}) that under the previous hypotheses, one are able to enumerate \emph{downward-closed sets} (by their finite decomposition in ideals), to decide inclusion between downward-closed sets and to decide if a state belongs to a given finite set of ideals. But the five properties are not sufficient to compute the complementary and the intersection of downward-closed sets.
%
Halfon introduced \emph{ideally-effective wqo} as wqo that essentially allow to compute representations of (principal) ideals $\mathop{\downarrow} s$, of the complementary of an ideal, of the complementary of filters (a filter is a set $\mathop{\uparrow} s$ for $s \in S$) and to compute representations of finite intersections of filters and finite intersections of ideals. Most well-known wqo are ideally-effective . \cite{DBLP:phd/hal/Halfon18}.
%	 (hence of downward-closed sets).
